One page description

### 2016-11-28 publications/Journal/3-features.tex
Summary of changes: - add proposed reply to reviewers - update abstract, introduction to mention PDEVS explicitly as a protocol compl$ - detail in a subsection implementation of PDEVS - detail our usage of parameter q Complete todo from previous review.

>>>>

% protocol or inherent parallelism?
\subsubsection{PDEVS}
In our tool each synchronization kernel is capable of executing its transitions in parallel. A configurable number of threads is allocated to optimally divide the processing load of concurrent transitions. The parallel execution of transitions introduces some overhead in thread pooling and locking, and disallows some optimizations in optimally rescheduling models. The concurrency of events and the combined computational load of the transitions has to outweigh this overhead to obtain a significant speedup, as we will demonstrate in Section~\textsc{\nameref{sec:4-performance}}.

### 2016-11-28 publications/Journal/4-performance.tex
Summary of changes: - add proposed reply to reviewers - update abstract, introduction to mention PDEVS explicitly as a protocol compl$ - detail in a subsection implementation of PDEVS - detail our usage of parameter q Complete todo from previous review.

\paragraph{Model}
We have opted to use the \textit{Queue} model for this comparison, as it allows for many interesting configurations.
%TODO what is meant with this allocation of threads and synchronized kernels?
The effect of combining 4 synchronized kernels, with each 4 threads for PDEVS, is contrasted with 16 threads for PDEVS and 16 kernels for conservative and optimistic.
This allows us to observe which is more efficient in obtaining a speedup.
We simulate a computational load by an optional call to sleep in the transition functions set at 5 milliseconds.
The model is configured with depth 4 and width 300 if the transition function has no load, and width 50 if the computational load is active.
In our configuration, an imminent model generates output, resulting in another model becoming imminent.
With respect to the theoretical analysis in~\cite{amdahlpdevs} this gives a parameter value $q = 1$.
Models are equally distributed over the kernels and between threads in PDEVS.
The coefficient of variation of our results is less than 1\%.
The communication overhead is hard to estimate, but given our coefficient of variation, we can expect this overhead to be constant.

>>>>

\paragraph{Model}
We have opted to use the \textit{Queue} model for this comparison, as it allows for many interesting configurations.
%TODO what is meant with this allocation of threads and synchronized kernels?
% 4 Kernels running on a dedicated thread, with per kernel 4 threads allocated to use for PDEVS.
The effect of combining 4 synchronized kernels, with each 4 threads for PDEVS, is contrasted with 16 threads for PDEVS and 16 kernels for conservative and optimistic.
The first scenario runs each kernel on a dedicated thread synchronized with the other 3 kernels. Each kernel can use up to 4 threads for PDEVS. In the second scenario PDEVS can use up to 16 threads while running in a sequential kernel. Finally 16 synchronized kernels are used with one thread per kernel.
This allows us to observe which is more efficient in obtaining a speedup.
We simulate a computational load by an optional call to sleep in the transition functions set at 5 milliseconds.
The model is configured with depth 4 and width 300 if the transition function has no load, and width 50 if the computational load is active.
In our configuration, an imminent model generates output, resulting in another model becoming imminent.
With respect to the theoretical analysis in~\cite{amdahlpdevs} this gives a parameter value $q = 1$. Q is the probability that a receiving model becomes immediately imminent (i.e. scheduled in the next timestep). 
Without random scheduling the receiving model becomes immediately imminent. With random scheduling the receiving model becomes imminent with a scheduled time in [1, timestep]. This would result in a probability $q = \frac{n}{timestep}$ with n the receiving models at that point in time. The benchmarks are run sufficiently long enough to guarantee that the frequency of internal and external transitions is equal between random and non-random benchmarks. This results in n equal to all models in the benchmark. Only the concurrency of events differs. 
Models are equally distributed over the kernels and between threads in PDEVS.
The coefficient of variation of our results is less than 1\%.
The communication overhead is hard to estimate, but given our coefficient of variation, we can expect this overhead to be constant.

### 2016-11-28 publications/Journal/abstract.tex
Update title
Summary of changes: - add proposed reply to reviewers - update abstract, introduction to mention PDEVS explicitly as a protocol compl$ - detail in a subsection implementation of PDEVS - detail our usage of parameter q Complete todo from previous review.

With the ever increasing complexity of simulation models, parallel simulation becomes necessary to perform simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++11 and based on PythonPDEVS, supporting both conservative and optimistic synchronization protocols.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol.
A comparison is made to adevs in terms of CPU time and memory usage, to show that our modularity does not hinder performance.
We further allow for an external component to gather simulation statistics, on which runtime switching between the different synchronization protocols can be based.
Model allocation is also studied to see how our conservative and optimistic synchronization protocols are affected by good and bad allocations.

>>>>

With the ever increasing complexity of simulation models, parallel simulation becomes necessary to perform simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++11 and based on PythonPDEVS, supporting both conservative and optimistic synchronization protocols.
The simulator not only supports both protocols but also has the capability to switch between them at runtime.
The simulator complements each of the synchronization protocols with the PDEVS protocol.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol.
A comparison is made to adevs in terms of CPU time and memory usage, to show that our modularity does not hinder performance.
We compare the speedup obtained by synchronization with that of the inherent parallelism of PDEVS in isolation and combination, and contrast the results with the theoretical limits.
We further allow for an external component to gather simulation statistics, on which runtime switching between the different synchronization protocols can be based.
Model allocation is also studied to see how our conservative and optimistic synchronization protocols are affected by good and bad allocations.
